Information Sheet \\ {\large Learning Discrete-valued Bayesian Networks from Mixed Data}

### 2015-11-26 information_sheet.tex
updated and sending to mykel

\noindent
\textbf{Why is this an important contribution to the machine learning literature?}

@@

The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
Furthermore, emperical demonstrations show that the proposed method produces superior discretization schemes, evalated using the cross-validated log-likelihood.\\[0em]

>>>>

\noindent
\textbf{How is this a contribution to the machine learning literature?}

@@

The proposed method learns discretization policies for continuous variables from mixed data while taking the Bayesian network structure into account.
Prior Bayesian methods, such as MODL \citep{Boulle_2006, Lustgarten_2011}, only consider the discretization of a single continuous variable with respect to another single discrete variable.
The predominant existing method for discretizing continuous variables in Bayesian networks is based on MDL~\citep{Friedman_1996}, and has cubic runtime in the number of data samples.
The proposed method learns the discretization with quadratic runtime in the number of data samples, allowing it to more efficiently scale to larger datasets.
Furthermore, emperical demonstrations show that the proposed method produces superior discretization policies, which was objectively evalated using the cross-validated log-likelihood.\\[0em]
